---
title: "QIA Project"
author: "Huang, Yiyuan"
date: "October 12, 2020"
output:
  html_document: default
  pdf_document: default
---

### Note

In this file, all the variables with suffix **_CAT** is the categorized continuous variables by the following ?ules:

1)	Interpretation for estrogen (ER) / progesterone (PgR) testing:
*	Samples with 1-100% of tumor nuclei positive for ER or PgR are interpreted as **positive**.
*	A sample is considered **negative** for ER or PgR if <1% or 0%.

2)	Interpretation for ?ER2 (IHC) TESTING IN BREAST CANCER:
*	If the HER2 result is 3+, diagnosis is HER2 **positive**.
*	If the HER2 result is 2+, diagnosis is HER2 **Equivocal**.
*	If the HER2 result is 0 or 1+, diagnosis is HER2 **negative**.

3) HER2D17Z1_RATIO_CAT: (-inf, 2]? (2, inf)

4) HER2_COPYNUMBER: (-inf,4], (4,6], (6, inf)

### Aim 1: 
Summary statistics for Demographics features:
Variables: AGE, DIAGNOSIS, ER_HUMAN, PgR_HUMAN, HER2_HUMAN. 

```{r aim1, warning=FALSE, message=FALSE, echo=FALSE}
library(dplyr)
library(a?senal)
#library(qwraps2)
library(irr)
library(psych)
library(ggpubr)
library(DescTools)
library(multcompView)
library(lsmeans)
library(ggplot2)

#options(qwraps2_markup = "markdown")
#----------------------------READ DATA--------------------------
QIA <- r?ad.csv("E:/research_lili/QIA/data/QIA project final-OCT-2020.csv", header = T)

#-------------------------Aim 1-----------------------------
#Aim 1: Summary statistics for Demographics features:
#Variables: AGE, DIAGNOSIS, ER_HUMAN, PgR_HUMAN, HER2_HUMAN. ?#factorize DIAGNOSIS
QIA$DIAGNOSIS <- as.factor(QIA$DIAGNOSIS)
QIA$HER2_HUMAN <- as.factor(QIA$HER2_HUMAN)

#Make summary table by package "arsenal"
my_controls <- tableby.control(
  numeric.stats = c("meansd", "medianq1q3", "range", "Nmiss2"),
  cat.stats?= c("countpct", "Nmiss2"),
  stats.labels = list(
    meansd = "Mean (SD)",
    medianq1q3 = "Median (Q1, Q3)",
    range = "Min - Max",
    Nmiss2 = "Missing"
  )
)

table1 <- tableby(~AGE+ ER_HUMAN+ PgR_HUMAN+ HER2_HUMAN+ DIAGNOSIS, data=QIA, control = m?_controls)
summ <- summary(table1)

#Dichotomize ER_HUMAN and PgR_HUMAN:
#Negative if <1, otherwise positive
ER_HUMAN_CAT <- as.factor(QIA$ER_HUMAN>=1)
PgR_HUMAN_CAT <- as.factor(QIA$PgR_HUMAN>=1)
QIA <- QIA %>% mutate(ER_HUMAN_CAT, PgR_HUMAN_CAT) 
levels(?IA$ER_HUMAN_CAT) <- c("Negative", "Positive")
levels(QIA$PgR_HUMAN_CAT) <- c("Negative", "Positive")

#make summary table with "arsenal"
my_controls2 <- tableby.control(
  cat.stats = c("countpct", "Nmiss2")
)
table2 <- tableby(~ER_HUMAN_CAT + PgR_HUMAN_CA?, data = QIA, control = my_controls2)
summ_dich <- summary(table2)

```

```{r table1, echo = F}
knitr::kable(summ, format = "markdown", caption="Table 1: Summary statistics")
```

```{r table2, echo = F}
knitr::kable(summ_dich, format = "markdown", captio? = "Table 2: Summary statistics of dichotomized ER_HUAMN and PgR_HUMAN")
```

### Aim 2:
Correlation between the Human score of (ER_HUMAN, PgR_HUMAN, HER2_HUMAN) and the Digital image analysis score (ER_COREO, PgR_COREO, HER2_COREO). 

```{r aim2_1, echo=F?LSE}
#Aim 2: Correlation between the Human score of (ER_HUMAN, PgR_HUMAN, HER2_HUMAN) 
#       and the Digital image analysis score (ER_COREO, PgR_COREO, HER2_COREO)

#ER_HUMAN vs ER_COREO (both cont --- icc)
corr_ER <- icc(QIA %>% select(ER_HUMAN, ER_CORE?), model = "twoway", type = "agreement", unit = "single")



#PgR_HUMAN vs PgR_COREO (both cont --- icc)
corr_PgR <- icc(QIA %>% select(PgR_HUMAN, PgR_COREO), model = "twoway", type = "agreement", unit = "single")


#HER2_HUMAN vs HER2_COREO (both ordinal ?at --- stuart tau-c)
QIA$HER2_COREO <- as.factor(QIA$HER2_COREO)
#corr_HER2 <- StuartTauC(as.numeric(QIA$HER2_HUMAN), as.numeric(QIA$HER2_COREO), conf.level = 0.95)
#KAPPA_1 <- cohen.kappa(QIA %>% select(HER2_COREO, HER2_HUMAN))

QIA$HER2_COREO_CAT <- cut(?s.numeric(QIA$HER2_COREO)-1, breaks = c(-1,1.5,2.5,3.5),
                          labels = c("Negative", "Equivocal", "Positive"))
QIA$HER2_HUMAN_CAT <- cut(as.numeric(QIA$HER2_HUMAN)-1, breaks = c(-1,1.5,2.5,3.5),
                          labels = c("Ne?ative", "Equivocal", "Positive"))
#corr_HER2_new <- StuartTauC(as.numeric(QIA$HER2_HUMAN_CAT), as.numeric(QIA$HER2_COREO_CAT), conf.level = 0.95)

KAPPA_2 <- cohen.kappa(QIA %>% select(HER2_COREO_CAT, HER2_HUMAN_CAT))
```

* ER_HUMAN vs ER_COREO (both cont?nuous --- interclass correlation coefficient(ICC))

The concordance between ER_HUMAN and ER_COREO is **`r round(corr_ER$value, 2)`**(p=`r round(corr_ER$p.value,2)`) with corresponding 95% Confidence Interval (`r round(corr_ER$lbound,2)`, `r round(corr_ER$u?ound,2)`).

The scatter plot is shown below

```{r p1, echo=F, out.width="80%", fig.align="center"}
ggplot(QIA, aes(x=ER_HUMAN, y=ER_COREO)) + 
  geom_point() +
  ylab("Estrogen receptor digital image analysis score") +
  xlab("Estrogen receptor pathologis?s' score")
```

* PgR_HUMAN vs PgR_COREO (both continous --- ICC)

The concordance between PgR_HUMAN and PgR_COREO is **`r round(corr_PgR$value,2)`**(p=`r round(corr_PgR$p.value,2)`) with corresponding 95% Confidence Interval (`r round(corr_PgR$lbound,2)`,?`r round(corr_PgR$ubound,2)`).

The scatter plot is shown below

```{r p2, echo=F, out.width="80%", fig.align="center"}
p2 <- ggplot(QIA, aes(x=PgR_HUMAN, y=PgR_COREO)) + 
  geom_point() +
  ylab("Progesteron receptor digital image analysis score") +
  xla?("Progesteron receptor pathologists' score")
```

* HER2_HUMAN vs HER2_COREO (both categorical --- KAPPA / weighted KAPPA)

The concordance between HER2_HUMAN_CAT and HER2_COREO_CAT is **`r round(KAPPA_2$kappa,2)`** (Kappa) or **`r round(KAPPA_2$weighted.k?ppa,2)`** (Weighted Kappa). 

The contingency table is your **Table 3**.


### Aim 3

```{r aim3, echo=FALSE}
#Aim 3A: Correlation between HER2_COREO (Negative, equivocal and Positive) 
#        and the HER2_FISH (Negative and Positive). 
QIA$HER2_FISH[whi?h(QIA$HER2_FISH=="")] = NA
QIA_3 <- QIA %>%
  filter(!is.na(HER2_FISH))
QIA$HER2_FISH <- as.factor(QIA$HER2_FISH)
#QIA$HER2_COREO_CAT <- cut(as.numeric(QIA$HER2_COREO), breaks = c(0,1.5,2.5,3.5),
#                         labels = c("Negative", "Equivocal"? "Positive"))

#table(QIA$HER2_FISH, QIA$HER2_COREO_CAT)


#corr_COREO_FISH <- cohen.kappa(QIA %>% select(HER2_COREO_CAT, HER2_FISH))
#corr_3a <- StuartTauC(as.numeric(QIA$HER2_FISH), as.numeric(QIA$HER2_COREO_CAT), conf.level = 0.95)


#Aim 3B: Correlatio? between HER2_COREO (cat) and HER2D17Z1_RATIO (cont).---ANOVA

#type III anova 
fit_3b <- lm(HER2D17Z1_RATIO ~ HER2_COREO_CAT,  data = QIA %>% filter(HER2_COREO_CAT!="Negative"))
#summary(fit_3b)
p_3b <- anova(fit_3b)[1,5] #p-value for F-test

#Aim 3C: Cor?elation between HER2_COREO (cat) and HER2_COPYNUMBER (cont). ---ANOVA

fit_3c <- lm(HER2_COPYNUMBER ~ HER2_COREO_CAT, data = QIA %>% filter(HER2_COREO_CAT!="Negative"))
p_3c <- anova(fit_3c)[1,5] #p-value for F-test

#Aim 3D: Correlation between DIAGNOSIS ?CAT) 
#        and HER2_FISH (CAT)/ASCOCAP_Giudline_Groups (CAT).
#QIA$ASCOCAP_Giudline_Groups[which(QIA$ASCOCAP_Giudline_Groups == "")] = NA
#QIA$ASCOCAP_Giudline_Groups <- as.factor(QIA$ASCOCAP_Giudline_Groups)

#corr_DIAG_FISH <- cohen.kappa(QIA %>% sel?ct(DIAGNOSIS, HER2_FISH))
#corr_DIAG_ASCO <- cohen.kappa(QIA %>% select(DIAGNOSIS, ASCOCAP_Giudline_Groups))
```

#### Aim 3A
HER2_COREO_CAT (Negative, equivocal and Positive) vs HER2_FISH (show contingency table and Fisher's exact test)

* Contingency tab?e

```{r aim3_table, echo=F}
t1 <- table(QIA_3 %>% select(HER2_COREO_CAT, HER2_FISH))
t1
```

* Fisher's exact test (to test if two categorical variables are significantly correlated **in a small-sample case**)

```{r test1, echo=F}
fisher.test(t1)
```

Th? result shows that p-value = 0.3183 > 0.05, which means there is no evidence to show that they are significantly correlated.

#### Aim 3B
Correlation between HER2_COREO and HER2D17Z1_RATIO_CAT (both categorical with small sample size --- Fisher's exact tes?)

```{r 3b, echo=F, warning=F}
QIA$HER2D17Z1_RATIO_CAT <- cut(QIA$HER2D17Z1_RATIO, breaks = c(-Inf, 2, Inf))
t2 <- table(QIA %>% select(HER2D17Z1_RATIO_CAT, HER2_COREO_CAT))
t2
fisher.test(t2)
```

The result shows that p-value = 0.2734 > 0.05, which mean? there is no evidence to show that they are significantly correlated.

#### Aim 3C
Correlation between HER2_COREO and HER2_COPYNUMBER (both categorical with small sample size --- Fisher's exact test)

```{r 3c, echo=F, warning=F}
QIA$HER2_COPYNUMBER_CAT <-?cut(QIA$HER2_COPYNUMBER, breaks = c(-Inf, 4, 6, Inf))
t3 <- table(QIA %>% select(HER2_COPYNUMBER_CAT, HER2_COREO_CAT))
t3
fisher.test(t3)
```

The result shows that p-value = 0.1281 > 0.05, which means there is no evidence to show that they are significant?y correlated.

### Aim 4
```{r aim4, echo=FALSE}
#Aim 4A: Discordant between the Human score of (ER_HUMAN, PgR_HUMAN, HER2_HUMAN) 
#and the Digital image analysis score (ER_COREO, PgR_COREO, HER2_COREO). 

#SAME AS BEFORE: CATEGORIZE COREO SCORES
ER_COREO_?AT = as.factor(QIA$ER_COREO>=0.01)
PgR_COREO_CAT = as.factor(QIA$PgR_COREO>=0.01)
QIA <- QIA %>% mutate(ER_COREO_CAT, PgR_COREO_CAT) 
levels(QIA$ER_COREO_CAT) <- c("Negative", "Positive")
levels(QIA$PgR_COREO_CAT) <- c("Negative", "Positive")

#corr_ER_CAT?<- StuartTauC(as.numeric(QIA$ER_HUMAN_CAT), as.numeric(QIA$ER_COREO_CAT), conf.level = 0.95)
#corr_PgR_CAT <- StuartTauC(as.numeric(QIA$PgR_HUMAN_CAT), as.numeric(QIA$PgR_COREO_CAT), conf.level = 0.95) 
corr_ER_CAT <- cohen.kappa(QIA %>% select(ER_HUMAN_CA?, ER_COREO_CAT))
corr_PgR_CAT <- cohen.kappa(QIA %>% select(PgR_HUMAN_CAT, PgR_COREO_CAT))
```

#### Aim 4A 
Discordance between the Human score of (ER_HUMAN, PgR_HUMAN, HER2_HUMAN) and the Digital image analysis score (ER_COREO, PgR_COREO, HER2_COREO). 

? ER_HUMAN_CAT vs ER_COREO_CAT (both categorical --- weighted KAPPA)

The concordance between ER_HUMAN_CAT and ER_COREO_CAT is **`r round(corr_ER_CAT$kappa,2)`** (Kappa) or **`r round(corr_ER_CAT$weighted.kappa,2)`** (weighted Kappa). 

The contingency tabl? is your **Table 1**.

* PgR_HUMAN_CAT vs PgR_COREO_CAT (both categorical --- weighted KAPPA)

The concordance between PgR_HUMAN_CAT and PgR_COREO_CAT is **`r round(corr_PgR_CAT$kappa,2)`** (Kappa) or **`r round(corr_PgR_CAT$weighted.kappa,2)`** (weighted ?appa). 

The contingency table is your **Table 2**.

* HER2_HUMAN VS HER2_COREO: the same as Aim 2.

#### Aim 4B 
Discordance between HER2_COREO and HER2_FISH: the same as 3A.

